Report

### 2021-03-03 Rmd/report.Rmd
Process data and merge old data'

# load data
stimuli.duration  <- fread(here("Data", "Stimuli", "stimuli_duration-aggregated.txt"))
data.sample       <- read_xlsx(here("Data", "Participant data", "data_participants.xlsx"))
data.fixations    <- fread(here("Data", "03_fixations.txt"))
attrition         <- fread(here("Data", "02_filtered-excluded-trials.txt"))
results           <- fread(here("Data", "05_gca-results.txt"))
predictions       <- fread(here("Data", "05_gca-predictions.txt"))
multicollinearity <- fread(here("Data", "05_gca-multicollinearity.txt"))
```

@@

@@

stimuli.duration %>%
	select(Location, Language, Version, TrialType, m_duration, sd_duration, mean_overlap) %>%
	kable(
		digits = 2,
		row.names = FALSE,
		col.names = c("**Location**", "**Language**", "**Version**", "**Trial type**", "***M* duration (s)**", "***SD***", "***M* overlap (s)***"),
		align = "c"
	)

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Audio duration. A) Distribution of audio durations by trial type, split by testing language and location. Boxplots indicate median duration, 25\\% and 75\\% percentiles, and maximum and minimum.  B) Distribution of overlap between audio and target-distractor presentation, split by testing language and location. C) Individual audio duration by word, split by trial type, testing language, and location. The dashed lines indicate the onset of target and distractor pictures presentation."}

include_graphics(here("Figures", "Stimuli", "duration-overlap.png"))

@@

We tested `r data.sample %>% filter(!Pilot, DateTest<now()) %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` we excluded. The final sample included `r data.sample %>% filter(!Pilot, DateTest<now(), Valid, LangProfile=="Monolingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` monolinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan monolinguals, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish monolinguals) and `r data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` bilinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan-dominant, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish-dominant).

>>>>

@@

```{r prepare, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# load data
stimuli <- readRDS(here("Results", "stimuli.rds"))
participants <- readRDS(here("Results", "participants.rds"))
gaze_trial <- readRDS(here("Results", "gaze_trial.rds"))
gaze_time <- readRDS(here("Results", "gaze_time.rds"))
attrition <- readRDS(here("Results", "attrition.rds"))
fit <- readRDS(here("Results", "fit_trials.rds"))
```

@@

## Intensity

## Pitch/F0

## Lexical frequency

@@

We tested `r distinct(participants, participant) %>% nrow()` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` were excluded. The final sample included `r data.sample %>% filter(!Pilot, DateTest<now(), Valid, LangProfile=="Monolingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` monolinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan monolinguals, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish monolinguals) and `r data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` bilinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan-dominant, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish-dominant).
